### 2022-11-13 NSF2022/Description/backgroundv3.tex

\begin{wrapfigure}[10]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}
In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

>>>>

\begin{wrapfigure}[16]{l}{4in} 
\includegraphics[width=4in]{figures/Background/coarsening.pdf}
\vspace{-20pt}
\caption{\label{fig:coarsening}
Modeling procedure.
We initilize a suspension of granules.
Under the moving domain problem
\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
with amphiphilic boundary condition, the granules
self-organize into vesicle bilayers.
We then introduce external hydrodynamic effects to study elastic properties.
}
\vspace{5pt}
\end{wrapfigure}
In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

\begin{wrapfigure}[10]{r}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}
Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.
